Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-12 automatica/paper.tex
wordings

Our work addresses challenging aspects of the control synthesis problem:  
we perform digital control synthesis over a ``hybrid model'',
namely a model encompassing a plant exhibiting continuous behavior, 
whereas the controller operates in discrete time and over a quantized domain.  
In particular, our model evaluates the effects of the quantizers (A/D and D/A
converters), as well as representation
errors introduced by the controller working  %% artifacts such as an
%% observer~\cite{astrom1997computer}
in a finite-precision domain. Our model also accounts for representation errors introduced
by our modelling of the plant using finite precision arithmetic. 
We reason safety requirements, which are frequently overlooked in conventional feedback control synthesis, but
play a key role in systems engineering, particularly for safety-critical applications of clear concern in modern autonomy contexts.

@@

  % Additions from CAV:
  % continuous time
  % floating point 
\item We automatically generate \emph{correct-by-construction} digital
  controllers using an inductive synthesis approach (CEGIS).  
  %% This application is non-trivial and addresses challenges specific to digital control
  %% systems, such as the presence of A/D quantizers and FWL operations.  
  In addition a stability property, the automatically computed state-feedback
  controllers must also guarantee a given safety specification.
  The implication is that, as opposed to existing
  methods for controller synthesis which rely on transfer function
  representations, we must consider a state-space representation of
  the physical system. Such a representation requires ensuring the
  specification over actual traces of the model, alongside the
  numerical soundness required by the effects of discretisation and
  finite-precision errors.

%%   \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
%%   function representations, which are inadequate to prove safety requirements. } 
%% %
\ifx\axelerator
\item We provide two novel algorithms: the first, a multi-staged approach, relies on 
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction/refinement and
  acceleration to improve scalability while retaining soundness.  %% A third
  %% algorithm evaluates systems using transfer functions where no state-space
  %% description is given.
  Both approaches provide sound synthesis of 
  feedback controllers and consider the various sources of imprecision in
  the implementation of the control algorithm and in the modeling of the
  plant. 
\else  
\item We present a novel multi-staged approach to synthesising digital controllers, using on 
  an unfolding of the dynamics up to a completeness threshold, and bit precise Bounded Model
  Checking to account for sources of imprecision in the implementation of the digital control algorithm
  and the modelling of the plant.
  \fi

@@

The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa} and related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}, 
synthesizes correct-by-design embedded control software for LTI models.    
It is based on the abstraction of the model to a finite-state machine, 
and on the formal control synthesis over safety- and reachability-based temporal properties thereon.  
%Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller software for a range of
%properties.  
The controller software can then be refined (implemented) over the concrete LTI model. 
%can be more complicated than
%the state-feedback control we synthesize, and the properties available cover more detail.  
However, relying on state-space discretization \mbox{Pessoa} is likely to incur in scalability limitations.   
%Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for
%continuous dynamics, and \cite{zamani2014} extends the approach to the Network Control Systems setup.

>>>>

Our work addresses challenging aspects of the control synthesis problem:  
we perform digital control synthesis over a ``hybrid model'',
namely a model encompassing a plant exhibiting continuous behavior, 
and a controller operating in discrete time and over a quantized domain.  
In particular, our model evaluates the effects of the quantizers (A/D and D/A
converters), as well as representation
errors introduced by the controller working  %% artifacts such as an
%% observer~\cite{astrom1997computer}
in a finite-precision domain. Our model also accounts for representation errors introduced
by our modelling of the plant using finite precision arithmetic. 
We reason about safety requirements, which are frequently overlooked in conventional feedback control synthesis, but
play a key role in systems engineering, particularly for safety-critical applications of clear concern in modern autonomy contexts.

@@

  % Additions from CAV:
  % continuous time
  % floating point 
\item We automatically generate \emph{correct-by-construction} digital
  controllers using an inductive synthesis approach (CEGIS).  
  %% This application is non-trivial and addresses challenges specific to digital control
  %% systems, such as the presence of A/D quantizers and FWL operations.  
  The automatically computed state-feedback
  controllers guarantee a given safety specification.
  The implication is that, as opposed to existing
  methods for controller synthesis which rely on transfer function
  representations, we must consider a state-space representation of
  the physical system. Such a representation requires ensuring the
  specification over actual traces of the model, alongside the
  numerical soundness required by the effects of discretisation and
  finite-precision errors.

%%   \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
%%   function representations, which are inadequate to prove safety requirements. } 
%% %
\ifx\axelerator
\item We provide two novel algorithms: the first, a multi-staged approach, relies on 
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction/refinement and
  acceleration to improve scalability while retaining soundness.  %% A third
  %% algorithm evaluates systems using transfer functions where no state-space
  %% description is given.
  Both approaches provide sound synthesis of 
  feedback controllers and consider the various sources of imprecision in
  the implementation of the control algorithm and in the modeling of the
  plant. 
\else  
\item We present a novel multi-staged approach to synthesising digital controllers, using 
  an unfolding of the dynamics up to a completeness threshold, and bit precise Bounded Model
  Checking to account for fixed-point arithmetic used in the implementation of the digital control algorithm
  and interval arithmetic to account for the imprecision in the modelling of the plant. 
  \fi

@@

The technique underpinning tools such as Pessoa~\cite{mazo2010pessoa}, related extensions \cite{Anta2010,liu16} and applications \cite{zamani2014}, 
synthesizes correct-by-design embedded control software for LTI models.    
It is based on the abstraction of the model to a finite-state machine, 
and on the formal control synthesis over safety- and reachability-based temporal properties thereon.  
%Based on this safety specification, \mbox{Pessoa} can synthesize embedded controller software for a range of
%properties.  
The controller software can then be refined (implemented) over the concrete LTI model. 
%can be more complicated than
%the state-feedback control we synthesize, and the properties available cover more detail.  
However, relying on state-space discretization \mbox{Pessoa} is likely to incur in scalability limitations.   
%Along this research line, \cite{Anta2010,liu16} studies the synthesis of digital controllers for
%continuous dynamics, and \cite{zamani2014} extends the approach to the Network Control Systems setup.
